### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Cryptography Libraries}
For symmetric ciphers, we evaluate \ctool{} on three types implementation of AES. For mebedTLS, we evaluate AES-NI and the reference implementation. We do not find any leakage sites in the AES-NI version. On the other hand, the reference implementation has several leakage sites. The bitsliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks. However, we find they only adopt the protection in the encryption function but leave the key
expansion function unprotected.

>>>>

\subsection{Cryptography Libraries}
For symmetric ciphers, we evaluate \ctool{} on three types of AES implementations. For mebedTLS, we evaluate AES-NI and the reference implementation. We do not find any leakage sites in the AES-NI version. On the other hand, the reference implementation has several leakage sites. The bitsliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks. However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected. The T-Table implementation has side-channel leakage sites in both the key expanding function and the actually encryption function. The result is similarly to the previous work.

We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors. We compare the result with previous work and find \ctool{} can identify all the leaked functions reported in the previous work.
